Conjure: Summoning Proxies from Unused Address Space

### 2019-09-01 paper/rebuttal.tex

\section{Letter To Reviewers}

We thank the reviewers for their detailed comments and insights. In this resubmission we have modified 
multiple items to address concerns and clarify various ambiguities raised by the previous submission. 
First we have modified sections \ref{sec:architecture} 
and \ref{sec:implementation} to better communicate the construction of the \scheme system, 
the modularity that it affords, and the benefits that we derive from it's properties. We 
have also added section \ref{sec:attacks} to discuss the security benefits and shortcomings 
of \scheme directly.

@@

Reviewers A, C, and D reference the difficulty of correctly mimicking realistic services with
reference to the mask site proxy option. We have added acknowledgement of the inherent difficulty of mimicking 
services in section \ref{sec:attacks} but note that we have multiple strong factors in our
favor. First we do not choose a single service to mimic as other works in the past have 
\cite{stegotorus, skypemorph, censorspoofer} making a fingerprinting attack more difficult to employ by effectively raising the noise
(false positive / false negative) rates on any classifiers. Second, there has been no indication 
of website fingerprinting being employed by censors to detect proxies in nation-state censorship 
efforts due to the cost of overblocking at scale.

We would like to underscore that mimicry is only a feature of a \scheme session when the client 
elects to use the mask site proxy option. A \scheme session that uses OSSH, Obfs4, etc. will 
not employ any mimicking. This heterogeneity is a strength as it allows \scheme to continue
providing secure proxy access to clients even when new active probing attacks are discovered for 
individual transports.

Reviewer D raises a concern about identifying phantom hosts by attempting to connect and
classifying based on the non-response of a host seen previously responding to a possible \scheme client. 
This would not be an effective attack on \scheme for multiple reasons. First, the internet is volatile,
and services come up, go down, or transition addresses regularly. Second, many networks are fire-walled
and require specific authentication and/or source address to access. Finally protocols on the internet
are diverse and may not reply when improperly probed. Simply checking whether a connection can be opened 
from a third party client will not indicate to a censor with reliable confidence that a client is 
contacting a phantom host.

All reviewers voice similar concerns about the incentives present for ISPs to deploy a system like
\scheme, and the burden that this may impose upon them. \scheme already has the cooperation of a 
a mid-sized transit ISP, and our test bench has demonstrated that this places
no undue burden upon them. Our system does not require any inline blocking or packet modification 
as we operate on packets mirrored to a machine that we host within the ISP's network. 
To clarify, the ISP is not responsible for finding unused addresses, discovering viable mask sites, 
or managing proxied connections -- we perform those operations on our station deployed
at an ISP. They are also not responsible for hosting sites (or managing certificates) at any of the 
phantom hosts, as \scheme does not host any fake services, connections to phantom hosts are 
redirected to the covert destination out of line. The only overhead 
for the ISP is providing our station (hosted locally in their network) with a TAP on the packets that 
pass by, ensuring that we do not create any bottleneck in the service that they provide to their customers.

As for the risk of refraction networking making the ISP a target for malicious activity, they likely already
are a target based on the information and access that they have and they work to make their networks 
secure against those attacks. The motivation of making the internet a more free and open environment,
low overhead of deployment, and the effective demonstration of \scheme in a production environment 
form a strong incentive.

We believe that \scheme represents a significant step forward in the arms race of proxy
discovery and censorship circumvention because we leverage the the unused addresses of the internet
to connect clients to secure, active probe resistant proxies without giving censors a singular 
specific IP address that can be blocked to inexpensively deny proxy access.

### 2019-09-01 paper/figures.tex
Architecture updates for paper.

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/conjure-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        Clients first register by sending a secret seed in a steganographic tag past the station in a
        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
        which the station responds as a phantom host application. If the client can prove knowledge of the
        seed used during registration, they are allowed access to the proxy. Otherwise,
        the phantom host application pretends to be a benign host by staying silent or forwarding traffic
        to a mask site to make it difficult for censors to distinguish phantom hosts from legitimate ones.
    }
    \label{fig:overview}
\end{figure}
}

@@

  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figures/dark-decoys}
    \vspace{-3pt}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
    \caption{\textbf{\scheme Operations}\,---\,\rm%
        A \scheme session is constructed in two pieces. First a client registers by sending a tls connection
        to the Decoy host (see Figure 2c) with a steganographically tagged payload.
        This registration contains the true address that the client would like to connect to and a seed 
        which the \scheme station uses to derive the Phantom IP address for the session(green dashed flow). 
        Second The client derives the same 
        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) that they specified in
        their registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
        and destination port (client IP, phantom IP, and phantom port respectively). The traffic is passed 
        to a proxy server handling the specific proxy specified by the client then redirected to the 
        covert address that the client indicated in their registration. 
        \\\hspace{\textwidth}
        Secrets for the individual proxy services are shared out of band or derived from the shared secret 
        between the client and the station such that an adversary attempting to probe a connection will be
        unable to connect to the proxy service. 
    }
    \label{fig:overview}
\end{figure}
}

@@

  \begin{subfigure}{\columnwidth}
    \label{fig:evolutionconjure}
    \includegraphics[width=\columnwidth]{figures/dark-decoys}
    \vspace{-3pt}
